\subsubsection{Expander Framework \& Clean Architecture Expander Requirements} \label{expander_framework_requirements}

In addition to the more generic requirements of previous sections, the following
requirements are specific for the Clean Architecture Expander \& Expander Framework artifact.

\requirement{The Expander Framework}
\begin{enumerate}[label=\themycounter.\arabic*]
    \item The Expander Framework enables interaction with the Clean Architecture Expander via a
    \gls{cli}. The \gls{cli} is implemented in the Presentation layer of the
    Expander Framework.
    \item The Expander Framework retrieves the model from an \gls{mssql} using the
    EntityFramework ORM technology. The EntityFramework technology is implemented in the
    Infrastructure layer of the Expander Framework.
    \item The Expander Framework loads and executes the configured Expanders. In the case of
    this research, only the Clean Architecture Expander is applied.
    \item The Expander Framework supports generic harvesting and injection, which can be
    used or extended by the Expanders using the \gls{ocp} principle.
    \item The Expander Framework supports generic template handling, which can be used or
    extended by the Expanders using the \gls{ocp} principle.
    \item The Expander framework adheres to this chapter's component and software Requirements
    specified in Sections \ref{component_requirements} and \ref{software_requirements}.
\end{enumerate}

\requirement{The Clean Architecture Expander}
\begin{enumerate}[label=\themycounter.\arabic*]
    \item The Clean Architecture Expander generates a C\# net7.0 RESTful service that provides an
    HTTP interface on top of the meta-model of the Expander Framework, allowing the basic
    \gls{crud} operations.
    \item The Clean Architecture Expander consists solely of an Application layer and reuses
    the Domain layer of the Expander Framework.
    \item The Clean Architecture Expander adheres to this chapter's component and software
    Requirements specified in Sections \ref{component_requirements} and
    \ref{software_requirements}.
\end{enumerate}
