\subsection{Expander Requirements} \label{expander_framework_requirements}

In addition to the more generic requirements outlined in previous sections, the following
requirements are specific to the Clean Architecture Expander and Expander Framework
artifact.

The Expander Framework facilitates interaction with the Clean Architecture Expander via a
command-line interface (CLI), which is implemented in the Presentation layer of the
framework. Additionally, the Expander Framework retrieves models from a Microsoft SQL
Server (MSSQL) database using EntityFramework ORM technology, integrated within the
Infrastructure layer. The framework also supports loading and executing configured
Expanders, though in this particular research, only the Clean Architecture Expander is
applied.

Moreover, the Expander Framework supports generic harvesting and injection
functionalities, which can be extended or used by the Expanders in accordance with the
Open-Closed Principle (OCP). This extensibility is further enhanced by the framework's
support for generic template handling, also designed to be extended by the Expanders
following the OCP. The framework adheres to the component and software requirements
outlined in Sections \ref{component_requirements} and \ref{software_requirements} of this
chapter.

The Clean Architecture Expander specifically generates a C\# .NET 7.0 RESTful service,
which provides an HTTP interface atop the Expander Framework’s meta-model, enabling basic
Create, Read, Update, Delete (CRUD) operations. This expander consists solely of an
Application layer and reuses the Domain layer provided by the Expander Framework.
Additionally, the Clean Architecture Expander adheres to the component and software
requirements set forth in Sections \ref{component_requirements} and
\ref{software_requirements} of this chapter.

By adhering to these requirements, both the Expander Framework and the Clean Architecture
Expander align with the overall architecture goals while maintaining flexibility and
extensibility.
